Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: correcting typos

We start by presenting our results for EdGB gravity.
%
In Fig.~\ref{fig:edgb_exec_sum} we show the margelized posteriors of the coupling constant $\ell_{\rm GB}$,
for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
QNM. The bottom panel panel shows the joint posterior combining both events.
%
We see for both events events the $N_{\rm max} = 0$ posteriors are characterized by a peak away from zero.
%
This does not mean that we are observing a deviantion from GR. We recall that the deviations from GR in the ParSpec framework
are controlled by $\gamma$, which here reads,
%
\begin{equation}
    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{\rm s}}\right)^4\,.
\end{equation}
%
As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior with maximum support near zero, indicating consistency
between data and GR.
%
We also observe that the inclusion of the spin corrections (i.e., $N_{\rm max} = 1$) displaces the posteriors towards
smaller values of $\ell_{\rm GB}$.

As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
must first check whether the ``EFT''~\eqref{eq:eft_bound} and
``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
%
We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown
the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$.
%
For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes past $0.2$, regardless of the mass scale $\mathfrak{m}$,
even at $\varepsilon = 1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is never met
at a significant credilibity and thus that we cannot place a bound on $\ell_{\rm GB}$.
%
The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not change when we include spin corrections to the EdGB QNM.
%
Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our present model}.

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov,
Serguei~Ossokine, Scott~E.~Perkins, and Helvi~Witek for discussions.
%
We also thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster and Steffen Grunewald for assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

>>>>

We start by presenting our results for EdGB gravity.
%
In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the coupling constant $\ell_{\rm GB}$,
for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
QNM. The bottom panel panel shows the joint posterior combining both events.
%
We see for both events events the $N_{\rm max} = 0$ posteriors are characterized by a peak away from zero.
%
This does not mean that we are observing a deviation from GR. We recall that
the deviations from GR in the ParSpec framework are controlled by $\gamma$,
which here reads,
%
\begin{equation}
    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{\rm s}}\right)^4\,.
\end{equation}
%
As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior with maximum support near zero, indicating consistency
between data and GR.
%
We also observe that the inclusion of the spin corrections (i.e., $N_{\rm max} = 1$) displaces the posteriors towards
smaller values of $\ell_{\rm GB}$.

As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
must first check whether the ``EFT''~\eqref{eq:eft_bound} and
``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
%
We check the validity of the EFT bound in Fig.~\ref{fig:edgb_cdf}. In the top (bottom) panel we show
the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$.
%
For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes
past $0.2$, regardless of the mass scale $\mathfrak{m}$, even at $\varepsilon =
1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
never met at a significant credibility and thus that we cannot place a bound on
$\ell_{\rm GB}$.
%
The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not
change when we include spin corrections to the EdGB QNM.
%
Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our
present model}.
%
These conclusions are summarized in Table~\ref{tab:summary_edgb}.

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele Berti, Andrea Maselli, Caio F. B. Macedo, Deyan Mihaylov,
Serguei Ossokine, Scott E. Perkins, and Helvi Witek for discussions.
%
We are grateful for the computational resources provided by the Max Planck
Institute for Gravitational Physics in Potsdam, specifically the
high-performace computing cluster Hypatia and to Steffen Grunewald for
assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%
